### 2017-12-12 CO681-QuantumInformationProcessing/project/matchings.tex
matching

$$\text{If $M_1$ and $M_2$ are matchings of size $s_1$ and $s_2$ respectively ($s_1 < s_2$) then there exist $s_2-s_1$ vertex disjoint $M_1$-augmenting paths.}$$

@@

@@

\subsection{Quantum Adversary}

>>>>

\begin{align*}&\text{If $M_1$ and $M_2$ are matchings of size $s_1$ and $s_2$ respectively ($s_1 < s_2$)}\\&\text{then there exist $s_2-s_1$ vertex disjoint $M_1$-augmenting paths.}\end{align*}

@@

\bigskip
\paragraph{Lower Bounds}
In \cite{boyer1996tight} and \cite{zhang2005power} they demonstrate the existence of a quantum adversary for maximum bipartite matching implying a $\Omega(n^{3/2})$ quantum query complexity lower bound for the problem. Since this is a special case of both general matching (to follow), and the network flow problem studied in the previous Section it provides a lower bound for those problems as well.

@@

Our general quantum matching algorithm follows the classic Blossom algorithm of Edmonds \cite{edmonds1965paths}. An excellent reference for this algorithm is Chapter $5$ of the textbook Combinatorial Optimization by Cook, Cunningham, Pulleyblank, and Schrijver \cite{cook2009combinatorial}. In broad strokes the algorithm starts with an empty matching $M$ and in each iteration identifies either an augmenting path, an odd circuit with one $M$-exposed vertex, or decides the matching is maximum and terminates. In the first case $M$ is augmented by the path found, and in the second the odd circuit is contracted to a single vertex and the algorithm proceeds on the resulting subgraph.
It can be shown that classically the Blossom algorithm can be implemented in time $O(nm\log n)$. The quantum algorithm presented in \cite{ambainis2006quantum} follows the same framework as the Blossom algorithm but speeds up all necessary searching by using Grovers Search. In every iteration of Blossom we have an exposed vertex $r$ and build a tree of vertices by breadth-first search which lie on alternating paths from $r$. Each vertex that lies on an even length path from $r$ in the tree is of interest. If an even vertex $v$ has an exposed neighbour then we have found an augmenting path. If it has an $M$-covered neighbour then we can either extend the tree or identify an odd circuit. These situations lead to three instances of Grover's Search at $v$ taking total expected time $O(\sqrt{nm})$.  This discussion leads to the following theorem, a detail proof of which is found in the source material.
A maximum matching can be found with a quantum computer in expected time $O(n^2(\sqrt{m/n} + \log n))$ in the list model and $O(n^{5/2}\log n)$ in the adjacency model.
